TaskDefinition

### 2020-02-20 Proposal.Rmd
Add GoogleDoc link to TaskDefinition

---
title: "TaskBoard"
author: "A group of fabulous contributors"
date: "2/19/2020"
output: html_document
---

@@

>>>>

---
title: "TaskDefinition"
author: "A group of fabulous contributors"
date: "2/19/2020"
output: html_document
---

@@

Given we will be collaborating on a single Rmd, I created a separate Google Doc at [here](https://docs.google.com/document/d/1O7t3q8Aik00dzFaNpWyqoNlxUk6Z0HkJLZuFpJmjpv4/edit?usp=sharing) 
just in case we would like to do parallel writing.
